Concurrent Programming with Harmony

### 2020-09-06 book/paper.tex
Latest

Harmony makes extensive use of dictionaries.
A dictionary maps values, known as \emph{keys}, to values.
The Harmony dictionary syntax and properties are a little different from Python.
Unlike Python, any Harmony value can be a key, including another
dictionary.
Harmony dictionaries are written as
$\mathtt{dict}\{ k_0: v_0, ~ k_1: v_1, ~ ... \}$.
If $d$ is a dictionary, and $k$ is a key, then the
following expression retrieves the Harmony value that $k$ maps to in $d$:
\begin{code}
$d$ $k$
\end{code}
This is unfamiliar to Python programers, but in Harmony square brackets can be used
in the same way as parentheses, so you can express the same thing in the form
that is familiar to Python programmers:
\begin{code}
$d$[$k$]
\end{code}
However, if $d$ = \texttt{dict\{ .count: 3 \}}, then you can write
can write $d$.\texttt{count} (which has value 3) instead of having to write
$d$\texttt{[.count]} (although both will work).
Thus using atoms, a dictionary can be made to look much like a Python object.
The meaning of $d$ $a$ $b$ $...$ is ((($d$ $a$) $b$) $...$).

@@

The first step is initialization.
It sets shared variable \textit{count} to 0 and
shared variable \textit{done} to \texttt{[False, False]}.
If we look at the next three steps, we see that:
\begin{itemize}
\item Process \texttt{implementer/0}
executed instructions 1 through 4, loading the value of
\textit{count} but stopping just before storing 1 into \textit{count};
\item Process \texttt{implementer/1}
executed instructions 1 through 11, storing 1 into
into \textit{count} and storing \texttt{True} into \textit{done}[1];
\item Process \texttt{implementer/0}
continues execution, executing instructions 5 through 11
storing value 1 into \textit{count}
and storing \texttt{True} into \textit{done}[0].
\end{itemize}
Finally, process \texttt{main()} runs and finds the problem.
This makes precise the concurrency issue that we encountered.

>>>>

Harmony makes extensive use of dictionaries.
A dictionary maps values, known as \emph{keys}, to values.
The Harmony dictionary syntax and properties are a little different from Python.
Unlike Python, any Harmony value can be a key, including another
dictionary.
Harmony dictionaries are written as
$\mathtt{dict}\{ k_0: v_0, ~ k_1: v_1, ~ ... \}$.
If $d$ is a dictionary, and $k$ is a key, then the
following expression retrieves the Harmony value that $k$ maps to in $d$:
\begin{code}
$d$ $k$
\end{code}
This is unfamiliar to Python programers, but in Harmony square brackets can be used
in the same way as parentheses, so you can express the same thing in the form
that is familiar to Python programmers:
\begin{code}
$d$[$k$]
\end{code}
However, if $d$ = \texttt{dict\{ .count: 3 \}}, then you can write
$d$.\texttt{count} (which has value 3) instead of having to write
$d$\texttt{[.count]} (although both will work).
Thus using atoms, a dictionary can be made to look much like a Python object.
The meaning of $d$ $a$ $b$ $...$ is ((($d$ $a$) $b$) $...$).

@@

The first step is initialization.
It sets shared variable \textit{count} to 0 and
shared variable \textit{done} to \texttt{[False, False]}.
If we look at the next three steps, we see that:
\begin{itemize}
\item Process \texttt{incrementer/0}
executed instructions 1 through 4, loading the value of
\textit{count} but stopping just before storing 1 into \textit{count};
\item Process \texttt{incrementer/1}
executed instructions 1 through 11, storing 1 into
into \textit{count} and storing \texttt{True} into \textit{done}[1];
\item Process \texttt{incrementer/0}
continues execution, executing instructions 5 through 11
storing value 1 into \textit{count}
and storing \texttt{True} into \textit{done}[0].
\end{itemize}
Finally, process \texttt{main()} runs and finds the problem.
This makes precise the concurrency issue that we encountered.
